### 2023-06-25 bachelorthesis/24-zonalflows.tex
#39: Sheraing rate plot in zonal flow chapter and presentation

The $\exb$ staircase pattern is manifest as radial structure formation in the $\exb$ shearing rate defined as\cite{Rath2016, Pueschel2008, Peeters2016}
\begin{equation}
	\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}~,
	\label{eq:shearingrate}
\end{equation}
where $\langle \phi \rangle$ is the zonal electrostatic potential normalized by $\rho_\ast T/e$ ($\rho_\ast = \rhoth/R$ is the thermal Larmor radius normalized with the major radius $R$, $T$ is the temperature and $e$ is the elementary charge).
The zonal potential is calculated from the electrostatic potential $\phi$ on the two-dimensional $\xcoord$-$\ycoord$-plane at the low field side according to Ref. \citenum{Rath2021}
\begin{equation}
\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)~.
\end{equation}
The $\exb$ shearing rate $\wexb$ is the radial derivative of the advecting zonal flow velocity \cite{Hahm1995, Waltz1998} and quantifies the zonal flow induced shearing of turbulent structures \cite{Biglari1990, Hahm1995, Burnell1997}. This type of structure is characterized by intervals of almost constant shear with alternating sign satisfying the Waltz criterion $|\wexb| \approx \gamma$\cite{Waltz1994, Waltz1998} ($\gamma$ is the growth rate of the most unstable linear ion temperature gradient (ITG)-driven Eigenmode), connected by steep flanks where $\wexb$ crosses zero. \\ \bigskip

@@

>>>>

The $\exb$ staircase pattern is manifest as radial structure formation in the $\exb$ shearing rate defined as\cite{Rath2016, Pueschel2008, Peeters2016}
\begin{equation}
	\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \xcoord^2}~,
	\label{eq:shearingrate}
\end{equation}
where $\langle \phi \rangle$ is the zonal electrostatic potential normalized by $\rho_\ast T/e$ ($\rho_\ast = \rhoth/R$ is the thermal Larmor radius normalized with the major radius $R$, $T$ is the temperature and $e$ is the elementary charge).
The zonal potential is calculated from the electrostatic potential $\phi$ on the two-dimensional $\xcoord$-$\ycoord$-plane at the low field side according to Ref. \citenum{Rath2021}
\begin{equation}
\langle \phi \rangle = \frac{1}{L_\ycoord} \int_0^{L_\ycoord} \mathrm{d}\ycoord ~ \phi(\xcoord,\ycoord,s=0)~.
\end{equation}
The $\exb$ shearing rate $\wexb$ is the radial derivative of the advecting zonal flow velocity \cite{Hahm1995, Waltz1998} and quantifies the zonal flow induced shearing of turbulent structures \cite{Biglari1990, Hahm1995, Burnell1997}. This type of structure is characterized by intervals of almost constant shear with alternating sign satisfying the Waltz criterion $|\wexb| \approx \gamma$\cite{Waltz1994, Waltz1998} ($\gamma$ is the growth rate of the most unstable linear ion temperature gradient (ITG)-driven Eigenmode), connected by steep flanks where $\wexb$ crosses zero [Fig. \ref{fig:shearingrate}]. \\ \bigskip

@@

\includegraphicsHere{Theory/Shearing-Rate.pdf}{
	Fully- and partially-developed pattern formation in the radial profile of the $\exb$ shearing rate as temporally averaged radial profiles of the $\exb$ shearing rate in near marginal ion temperature gradient-driven turbulence with adiabatic electrons and the growth rate $\pm\gamma$ of the most unstable linear ITG-driven Eigenmode. 
}{fig:shearingrate}{0.5}
